\section{Essential Equipment}

\begin{enumerate}
    \item Everybody in the crew probably has a \gls{Cortical Stack}, but who does have a \gls{Cyberbrain}, if not being an Infomorph? This changes handling dying quite a bit. If anyone does not have a Cyberbrain, take an \textbf{\gls{Ego Bridge}} onto the mission?

    \item Does everyone have their \textbf{\gls{Fake Ego ID}}, or really does not need one? If Farcasting everyone including the Infomorphs will likely need one. If travelling by ship anyone without one will need to be smuggled in, and won't be able to move freely -- plus might need to carry a decoy depending on area monitoring/ security.
\end{enumerate}


\section{Dependencies}

\begin{enumerate}
    \item Either (almost everyone) or nobody should have \textbf{TacNet}. “Tacnets allow a group and their muses/gear to share real-time tactical situational and sensory data over encrypted mesh channels. They are used by sports teams, security/military units, gamers, and anyone else that needs to coordinate actions. Tacnets provide the following functions: [...]”\footnote{To many for the page, obviously huge advantage to have every team member in one.} \citep[pg. 327]{ep2e_1.1_2019}

    \item \textbf{Spoofer} “Use spoof apps to fake transmissions and mesh IDs (Spoofing ▶247).” is almost\footnote{The rare exception would be when acquiring the spoofing data externally, either by hacking a device processing it, or acquiring it from someone else having used sniffing.} worthless without Sniffer \citep[pg. 326]{ep2e_1.1_2019}, as “To spoof signals, you must first successfully monitor an active connection between the two systems using a sniffer app (Sniffing ▶245).” (\citep[pg. 247]{ep2e_1.1_2019}).\citep[pg. 326]{ep2e_1.1_2019}

    \item \textbf{Exploit} “A hacker library/tool for taking advantage of known software vulnerabilities. Required for hacking.” \citep[pg. 326]{ep2e_1.1_2019} This is a necessary item (app) for anyone who wants to do any kind of hacking.\footnote{Which should mean strictly necessary for offensive. Would make some sense to have severe limitations in defense, too, though.}
\end{enumerate}


\section{Capabilities}

\subsection{Hacking}

\begin{enumerate}
    \item Member with high Infosec Skill.

    \item Member with high Interface Skill.

    \item Member with high Hardware: Electronics Skill (if meant to include dealing with disconnected or air gapped systems).
    
    \item \textbf{Exploit} “A hacker library/tool for taking advantage of known software vulnerabilities. Required for hacking.” \citep[pg. 326]{ep2e_1.1_2019} This is a necessary item (app) for anyone who wants to do any kind of hacking.\footnote{Which should mean strictly necessary for offensive. Would make some sense to have severe limitations in defense, too, though.}
\end{enumerate}